State and Parameter Estimation for Spatio-Temporal Neural Fields

### 2010-05-09 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
added abstract to paper

\address{$^1$ Department of Electrical and Electronic Engineering, University of Melbourne, Melbourne, Vic, 3010 Australia} \address{$^2$ Department of Automatic Control and Systems Engineering, University of Sheffield, Mappin Street, Sheffield, S1 3JD, UK} \address{$^3$ Department of Applied Physics and Applied Mathematics, Columbia University, US} \address{$^4$ Ken's} \ead{dfreestone@bionicear.org} 
\begin{abstract}
	Will do the abstract towards the end. 
\end{abstract}

>>>>

\address{$^1$ Department of Electrical and Electronic Engineering, University of Melbourne, Melbourne, Vic, 3010 Australia} \address{$^2$ Department of Automatic Control and Systems Engineering, University of Sheffield, Mappin Street, Sheffield, S1 3JD, UK} \address{$^3$ Department of Applied Physics and Applied Mathematics, Columbia University, US} \address{$^4$ Ken's} \ead{dfreestone@bionicear.org}

\begin{abstract}
	This paper presents a framework for creating patient specific neural field models from electrophysiological data. A basis function decomposition of the Wilson and Cowen or Amari style neural field equations is used to form a state space model. Spatial frequency analysis methods are used for model selection, by systematically specifying the basis function configuration required to capture the dominant characteristics of the neural field with the reduced finite dimensional model. Using the neural field model equation with modelled sensors, we generate data used to illustrate the state and parameter estimation framework. This framework provides a link between patient specific neurophysiological data and theoretical neural fields models. This link may lead to greater understanding of cortical dynamics at the meso and macroscopic scale where diseases such as epilepsy are manifested.   
\end{abstract}
